### 2020-10-02 README.Rmd
Opps little edit

```{r, eval = run_bw}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("libe", "caca", "astr", "litu", "havi", "cagl", "cato")
)
```

```{r, eval = run_bw}
posterior_plots_scbi[["lambda"]]
```

>>>>

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("libe", "caca", "astr", "litu", "havi", "cagl", "cato")
)
```

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
```
